---
title: "Multiple waves"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multiple waves}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(aedseo)
```

## Methodology

This method uses the seasonal onset and burden level methodology to estimate multiple waves for diseases that do not follow a one peak per season pattern.
The burden levels are used to define when the first wave has ended by droping below the desired intensity breakpoint whereafter a new wave can start.
The seasonal onset method is used to determine each wave onset - in the same way as for the single seasonal onset.

The `combined_seasonal_output()` function implements this functionallity by defining the following variables:

- $\text{multiple_waves}$: A logical. Should the output contain multiple waves?
- $\text{burden_level_decrease}$: A character string specifying the burden breakpoint the observations should decrease below before a new increase in observations
can call a new wave onset if seasonal onset criteria are met. Choose between; "very low", "low", "medium", or "high".
- $\text{steps_with_decrease}$: An integer specifying how many time steps (days, weeks, months) the decrease should be observed under the `burden_level_decrease`
before starting the search for a new wave onset.

## Applying the multiple waves algorithm
As an example we first generate cases in a `tsd` object, with the `generate_seasonal_data()` function. Then we rescale time from monthly to weekly observations to get multiple waves.
```{r, echo = FALSE, dpi=300}
# Construct an 'tsd' object with time series data by imputing multiple waves per season
set.seed(222)
tsd_data_monthly <- generate_seasonal_data(
  years = 14,
  phase = 3,
  start_date = as.Date("2020-05-18"),
  noise_overdispersion = 5,
  time_interval = "months"
)

tsd_data <- to_time_series(
  cases = tsd_data_monthly$cases,
  time = seq.Date(
    from = as.Date("2020-05-18"),
    by = "week",
    length.out = length(tsd_data_monthly$cases)
  )
) |>
  dplyr::filter(time < as.Date("2023-05-22"))
plot(tsd_data)
```

### Estimate disease-specific threshold
```{r}
disease_threshold <- estimate_disease_threshold(tsd_data)
```

### Estimate multiple waves
```{r}
multiple_waves <- combined_seasonal_output(
  tsd_data,
  disease_threshold = disease_threshold$disease_threshold,
  multiple_waves = TRUE,
  burden_level_decrease = "low",
  steps_with_decrease = 2
)
```

### Plot the comprehensive seasonal analysis with multiple waves
```{r, echo = FALSE, dpi=300}
plot(multiple_waves)
```
